---
title: "Miyauna Parent/Offspring Regression"
author: "Drafted by Miyauna and edited by Dai"
output:
  html_document: default
  pdf_document: default
date: "2023-12-08"
---

The R codes within the R Markdown document has to be inside "code chunks" that start with 

` ```{r} `

and end with

` ``` `

Then, the code that appears between those lines are executed when you "knit" the document. 

```{r}
parents=read.csv("Paramecium_Phenotype_Data_Parents.csv")
offspring=read.csv("Paramecium_Phenotype_Data.csv")
```

```{r}
head(parents)
```

```{r}
head(offspring)
```

```{r}
library(tidyverse)
```

## parent/offspring regression for area

Here is the file names in the "offspring" data:

```{r}
unique(offspring$file)
```

First, I removed varaibles from the offspring names to make it easier to compare to the parents using the mutate function

```{r}
offspring_mean=offspring %>% group_by(file) %>% 
  summarise(area=mean(mean_area)) 

offspring_mean
```

```{r}

offspring_id=pull(offspring_mean, file)

```

I then replaced the irrelvent identification variable in the parent id with a blank space using the mutate function

I did the above for parents 1 and 2

```{r}
parent1=offspring_id %>% str_replace("M_F2_", "") %>% str_split("x", simplify=T) 
p1=parent1[,1]

parent2=parent1[,2] %>% str_split("_", simplify=T) 
p2=parent2[,1]
```

```{r}
offspring_mean=offspring_mean %>% mutate(parent1=p1) %>% mutate(parent2=p2) %>% mutate(offspring_area=area) %>% select(-area)
```

```{r}
offspring_mean
```

### I created unique files for the offspring and parent areas with the new names 

```{r}
parents_area=parents%>%group_by(file) %>% 
  summarise(area=mean(mean_area)) %>%
  mutate(parents_id=str_replace(file, "M_PC_23_G_", "")) %>%
  select(-file)
```


I joined the files together using the left join function

```{r}
area_data=offspring_mean %>% left_join(., parents_area, by=join_by(parent1==parents_id)) %>%
left_join(., parents_area, by=join_by(parent2==parents_id)) %>% 
  mutate(midparent_area=(area.y+area.x)/2)


#parents_id=pull(parents_mean, file) %>% str_replace("M_PC_23_G_", "")
```

Then I ran the actual regression analysis

```{r}
po_reg_area<-glm(area_data$offspring_area~area_data$midparent_area)
summary(po_reg_area)
```

### lastly i ploted the graph using ggplot 

```{r}
ggplot(data=area_data,aes(x=midparent_area, y=offspring_area))+
  geom_point()+
  geom_smooth(method=glm)
```

